---
pagetitle: "Backwards Std Normal Right Tail Area"
params:
  area: 0.18
---

```{r}
library("statplosion")
area<-params$area; 
```

```{r echo=FALSE}
left_area <- 1.0-area
z <- qnorm(left_area)
z_rounded <-round(z,2) 
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```

We want to find the z-value for a given right tail area of $`r 100*area`\%$. 
    
This is an example of a **backwards** problem, since we are going from an **area to a z-value**.

Here is what the picture looks like: 

```{r fig.height=2, fig.width=3.5, fig.align="center"}
std_normal_curve()
std_normal_shade_right_area(z)
std_normal_label_point(z, label="z=?")
```
     
The shaded right tail area corresponds to **`r 100*area`%** of the data.   
     
Now we can't just look up the area in the z-table since **the table only has left tails** and we have a right tail. 

But we have this:

$$
\text{left tail} =  1.0 - \text{right tail}
$$

So instead of looking for a right tail of size **`r area`**, we can look for a left tail of size **`r left_area`**.  

We look through the table and **_look for the area that is closest_** to the value **`r 100*left_area`%** which we need.    
    
We might not find this value exactly but lets locate the closest value that we can:

```{r}
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
make_highlighted_z_huxtable(z, 1)
```

So that means we can take:

$$
z =`r z_rounded`
$$

as our solution. That is the z-value that we need. 

Here is the picture then:

```{r fig.height=2, fig.width=3.5, fig.align="center"}
std_normal_curve()
std_normal_shade_right_area(z_rounded)
std_normal_label_point(z_rounded)
```

