---
pagetitle: "Backwards Std Normal Left Tail Area"
params:
  area: 0.10
---

```{r}
library("statplosion")
area<-params$area; 
```

```{r echo=FALSE}
z <- qnorm(area)
z_rounded <-round(z,2) 
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```
We want to find the z-value for a given left tail area of $`r 100*area`\%$. 

This is an example of a **backwards** problem, since we are going from an **area to a z-value**.

Here is what the picture looks like: 
    
```{r fig.height=2, fig.width=3.5, fig.align="center"}
std_normal_curve()
std_normal_shade_left_area(z)
std_normal_label_point(z, label="z=?")
```
     
The shaded left tail area corresponds to **`r 100*area`%** of the data.  We use the standard normal table to find the z-value that goes with this left tail.   

We look through the table and **_look for the area that is closest_** to the value **`r 100*area`%** which we need.    
    
We might not find this value exactly but we locate the closest value that we can:

```{r}
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
make_highlighted_z_huxtable(z, 1)
```
So that means we can take:

$$
z =`r z_rounded` 
$$

as our solution. That is the z-value that we need. 

Here is the picture then:

```{r fig.height=2, fig.width=3.5, fig.align="center"}
std_normal_curve()
std_normal_shade_left_area(z_rounded)
std_normal_label_point(z_rounded)
```

