---
pagetitle: "Confidence Interval for Means"
params:
  xbar: 12.4 
  s: 5.1 
  n: 38 
  confidence: 0.99
---

```{r}
xbar<-params$xbar
s<-params$s
n<-params$n
confidence<-params$confidence
```

```{r include=FALSE}
tstar <- qt(confidence + (1.0-confidence)/2.0,df=n-1) 
E <- tstar*s/sqrt(n)
xbarMinusE <- xbar - E
xbarPlusE <- xbar + E
```

First we will calculate the $t^\star$ involved, using the confidence level `r confidence*100`%. 

In a spreadsheet we do the following:

**=TINV(1.0-confidence, n-1)**

Since $n=`r n`$, in this case this will look like this:

**=TINV(`r 1.0-confidence`, `r n-1`)**

If we do this we get 

$$
t^\star = `r tstar`
$$

We now plug into the formula for E using the sample standard deviation, the sample size and the $t^\star$:

$$
E=(t^\star)\frac{s}{\sqrt{n}} 
 =(`r tstar`)\frac{`r s`}{`r sqrt(n)`}
 = `r E` 
$$

Then we find the two endpoints.    
   
The left one is this:

$$
\bar x - E = `r xbar`-`r E` = `r xbarMinusE` 
$$

The right one is this:

$$
\bar x + E = `r xbar`+`r E` = `r xbarPlusE` 
$$

So the confidence interval for this sample mean is: 

$$
(`r round(xbarMinusE,2)`,`r round(xbarPlusE,2)`) 
$$

