---
pagetitle: "Confidence Interval for Proportions"
params:
  count: 201 
  n: 518
  confidence: 0.95
---

```{r}
count<-params$count
n<-params$n
phat<-count/n
qhat<- 1-phat
confidence<-params$confidence
```

```{r include=FALSE}
zstar <- round(-1*qnorm((1.0-confidence)/2.0),3) 
E <- round(zstar*sqrt((1-phat)*phat/n ),3)
phatMinusE <- phat - E
phatPlusE <- phat + E
leftEndPtPercent <- round(100*phatMinusE)
rightEndPtPercent <- round(100*phatPlusE)
```

The sample proportion is $`r count`$ out of $`r n`$:

$$
\hat p = \frac{count}{n} = \frac{`r count`}{`r n`} = `r phat` 
$$

Before we start we check the conditions showing we can use z-values from a standard normal distribution here: $n(\hat p)=(`r n`)(`r phat`)= `r n*phat`$ and $n(1-\hat p)=(`r n`)(`r qhat`)= `r n*qhat`$

Since these are both at least $5$ we are in good shape.

Next we will calculate the $E$ involved, using the confidence level `r confidence*100`%. 

For this confidence level we can look up that the appropriate critical value $z^\star$ to use. In this case it is $z^\star = `r zstar`$.

We plug the sample proportion $\hat p=`r phat`$ and the sample size $n=`r n`$ and the $z^\star$ into our formula for $E$:

$$
E=(z^\star)\sqrt{\frac{(1-\hat p)(\hat p)}{n}} 
 =(`r zstar`)\sqrt{\frac{(1-`r phat`)(`r phat`)}{`r n`}}
 = `r E` 
$$

Then we find the two endpoints.    
   
The left one is this:

$$
\hat p - E = `r phat`-`r E` = `r phatMinusE` 
$$

The right one is this:

$$
\hat p + E = `r phat`+`r E` = `r phatPlusE` 
$$

So the confidence interval for the sample proportion is 

$$
(`r phatMinusE`,`r phatPlusE`) 
$$

If we wanted this rounded to the nearest percent we would use:

$$
(`r leftEndPtPercent` \% ,`r rightEndPtPercent` \%) 
$$

We could say the confidence interval is from $`r leftEndPtPercent` \%$ to  $`r rightEndPtPercent` \%$.
