---
pagetitle: "Hypothesis Testing - Proportions Left Tail Test"
params:
  count: 190 
  n: 250 
  p: 0.79
---

```{r}
library("statplosion")
```

```{r}
p<-params$p
q<-1-p
count<-params$count
n<-params$n 
phat<-count/n
stdev <- sqrt((1-p)*p/n)
numer <- phat-p
z <- round(numer/stdev,2)
area <- round(pnorm(z),4)
nearestPercent <- round(area*100)
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```

The claim about the population proportion involves $`r p`$.

Here are the null and the alternative hypotheses:

\begin{align}
H_0:p &= `r p` \\
H_a:p &< `r p` 
\end{align}

- The null hypothesis says **The population proportion is $`r p`$**
- The alternative hypothesis says **The population proportion is less than 
$`r p`$**

Before we start we check the conditions of the Central Limit Theorem to make sure we can use a normal distribution here:

$np=(`r n`)(`r p`)= `r n*p`$ and $n(1-p)=(`r n`)(`r q`)= `r n*q`$

Since these are both at least $5$ we are in good shape.

Now if the null hypothesis is true, the Central Limit Theorem says the sampling distribution of sample proportions would look like this:

```{r fig.height=2, fig.width=3, fig.align="center"}
normal_curve(p,round(stdev,4), show=FALSE, axis_label=bquote(hat(p)))
```

Next we look at our test statistic, which is just our sample proportion:

$$
\hat p = \frac{count}{n} = \frac{`r count`}{`r n`} = `r phat` 
$$

So we want to know how likely it is to get a sample proportion of `r phat` in this situation.  

In fact the **P-value is just this left tail area**

```{r fig.height=2, fig.width=3, fig.align="center"}
normal_curve(p,round(stdev,4), show=FALSE, axis_label=bquote(hat(p)))
normal_shade_left_area(round(phat,4),p,round(stdev,4))
normal_label_point(round(phat,4))
```

We want the shaded **_left tail area_** that is to the left of $\hat p = `r phat`$:

We will find this area by changing the sample proportion $\hat p$ into a z-value and using the standard normal table. 

First we need the calculation of the standard deviation since we need this in our z-value calculation:

$$
\small{
stdev=\sqrt{\frac{(1-p)p}{n}} 
 =\sqrt{\frac{(1-`r p`)`r p`}{`r n`}}
 =\sqrt{\frac{(`r (1-p)`)`r p`}{`r n`}}
 =\sqrt{\frac{`r (1-p)*p`}{`r n`}}
 =`r stdev` 
 }
$$

Now lets find the z-value using the sample proportion $\hat p= `r phat`$, the population proportion $p=`r p`$ and the standard deviation $stdev$ we just found:

$$
z=\frac{\hat p-p}{stdev}
 =\frac{`r phat`-`r p`}{`r stdev`}
 =\frac{`r numer`}{`r stdev`}
 =`r z` 
$$

So here is the equivalent left tail area for of $z=`r z`$. 

```{r fig.height=2, fig.width=3, fig.align="center"}
std_normal_curve()
std_normal_shade_left_area(z)
std_normal_label_point(z)
```

This area is the same size as our original area so we just find this one using the standard normal distribution.

We can look up the area in the standard normal z-table using $z=`r z`$  
    
We go to the row that has `r u` and then to the column that contains `r h` and we see this: 

```{r}
make_highlighted_z_huxtable(z, 1)
```

So that means the **P-value** we need in this situation is:

$$
P = \text{left tail area} =`r area` 
$$

So based on this our conclusion is that this is **`r hypothesis_test_conclusion(area)` against the null hypothesis**.


