---
pagetitle: "Hypothesis Testing - Means Left Tail Test"
params:
  xbar: 98
  n: 15 
  mu: 110 
  s: 20 
---

```{r}
library("statplosion")
```

```{r}
mu<-params$mu
xbar<-params$xbar
n<-params$n 
s<-params$s
stderr<-s/sqrt(n)
numer <- xbar-mu
t <- round(numer/stderr,2)
area <- round(pt(t, n-1),4)
nearestPercent <- round(area*100)
parts <- extract_tenths_and_hundredths(t)
u <- parts[1]
h <- parts[2]
```
We have $\bar x = `r xbar`$, $s = `r s`$ and $n=`r n`$. 

The claim about the population mean involves $`r mu`$.

Here are the null and the alternative hypotheses:

\begin{align}
H_0:\mu &= `r mu` \\
H_a:\mu &< `r mu` 
\end{align}

- The null hypothesis says **The population mean is $`r mu`$**
- The alternative hypothesis says **The population mean is less than 
$`r mu`$**

We want to know how likely it is to get a sample mean of `r xbar` in this situation.  
    
We will estimate this by finding a t-value for the sample mean $\bar x$ and then using the t-distribution to find the left tail area.   

We have to use a t-value and the t-distribution because we do not have the population standard deviation ($\sigma$) in this case and only have a sample standard deviation $s$.  

We find the t-value using the sample mean $\bar x= `r xbar`$, the population mean $\mu=`r mu`$, and the sample standard deviation $s = `r s`$:

$$
t=\frac{\bar x-\mu}{\frac{s}{\sqrt{n}}}
 =\frac{`r xbar`-`r mu`}{\frac{`r s`}{\sqrt{`r n`}}}
 =\frac{`r numer`}{`r stderr`}
 =`r t` 
$$

Now you can compute the left tail area which is our p-value in a spreadsheet using the TDIST function:

**=TDIST(ABS(t), n-1, 1)**

We put in $t=`r t`$ and $n=`r n`$:

**=TDIST(ABS(`r t`), `r n`-1, 1)**

or 

**=TDIST(`r abs(t)`, `r n-1`, 1)**

We get $`r area`$ as a result and this is our P-value: 

$$
P = \text{left tail area} =`r area` 
$$

So based on this our conclusion is that this is **`r hypothesis_test_conclusion(area)` against the null hypothesis**.


