---
pagetitle: "Hypothesis Testing - Means Left Tail Z Test"
params:
  xbar: 98 
  n: 15 
  mu: 110 
  sigma: 20 
---

```{r}
library("statplosion")
```

```{r}
mu<-params$mu
xbar<-params$xbar
n<-params$n 
sigma<-params$sigma
stderr<-sigma/sqrt(n)
numer <- xbar-mu
z <- round(numer/stderr,2)
area <- round(pnorm(z),4)
nearestPercent <- round(area*100)
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```

We have $\bar x = `r xbar`$, $\sigma = `r sigma`$ and $n=`r n`$. 

The claim about the population mean involves $`r mu`$.

Here are the null and the alternative hypotheses:

\begin{align}
H_0:\mu &= `r mu` \\
H_a:\mu &< `r mu` 
\end{align}

- The null hypothesis says **The population mean is $`r mu`$**
- The alternative hypothesis says **The population mean is less than 
$`r mu`$**

If the null hypothesis is true, then by the Central Limit Theorem the sample distribution of sample means would look like this:

```{r fig.height=2, fig.width=3, fig.align="center"}
normal_curve(mu,round(stderr,4), show=FALSE, axis_label=bquote(bar(x)))
```

The above is true because we have the population standard deviation $\sigma$ and so we can use a z-value and z-distribution to do our calculations below. 

We want to know how likely it is to get a sample mean of `r xbar` in this situation.  

$$
z=\frac{\bar x-\mu}{\frac{\sigma}{\sqrt{n}}}
 =\frac{`r xbar`-`r mu`}{\frac{`r sigma`}{\sqrt{`r n`}}}
 =\frac{`r numer`}{`r stderr`}
 =`r z` 
$$

Now you can compute the left tail area which is our p-value in a spreadsheet using the NORMSDIST function:

**=NORMSDIST(z)**

Now putting in the $z$-value we got: 

**=NORMSDIST(`r z`)**

We get $`r area`$ as a result and this is our P-value: 

$$
P = \text{left tail area} =`r area` 
$$

So based on this our conclusion is that this is **`r hypothesis_test_conclusion(area)` against the null hypothesis**.
