---
pagetitle: "Normal Area Between"
params:
  mu: 23
  sigma: 8 
  x1: 10
  x2: 25
---

```{r}
library("statplosion")
```



```{r}
x1<-params$x1; 
x2<-params$x2; 
mu<-params$mu; 
sigma<-params$sigma; 
numer1<-(x1-mu); 
numer2<-(x2-mu); 
z1 = (x1-mu)/sigma
z2 = (x2-mu)/sigma
```

```{r echo=FALSE}
area1_actual <- pnorm(z1)
area1_rounded <- round(area1_actual,4)
nearest_percent1 <- round(area1_rounded*100)

area2_actual <- pnorm(z2)
area2_rounded <- round(area2_actual,4)
nearest_percent2 <- round(area2_rounded*100)

area_between <- area2_rounded - area1_rounded
nearest_percent_between <- round(area_between*100)
```
We have mean $\mu=`r mu`$, $\sigma=`r sigma`$, $x_1 = `r x1`$ and $x_2 = `r x2`$:

Here is the picture of the area we want.  

```{r fig.height=2, fig.width=3.5, fig.align="center"}
normal_curve(mu,sigma)
normal_shade_area_between(x1,x2,mu,sigma)
normal_label_point(x1)
normal_label_point(x2)
```

We want the shaded region between $x_1=`r x1`$ and $x_2 = `r x2`$

So we first compute the z-values for each of these x-values:

First let's do $x_2=`r x2`$: 

$$
z_2=\frac{x-\mu}{\sigma}
 =\frac{`r x2`-`r mu`}{`r sigma`}
 =\frac{`r numer2`}{`r sigma`}
 =`r round(z2,2)` 
$$

Then let's do $x_1=`r x1`$: 

$$
z_1=\frac{x-\mu}{\sigma}
 =\frac{`r x1`-`r mu`}{`r sigma`}
 =\frac{`r numer1`}{`r sigma`}
 =`r round(z1,2)` 
$$
    
So here is the equivalent shaded region for the standard normal curve:  
    
```{r fig.height=2, fig.width=3.5, fig.align="center"}
std_normal_curve()
std_normal_shade_area_between(z1,z2)
std_normal_label_point(round(z1,2))
std_normal_label_point(round(z2,2))
```

Now using the table we get the left tail area for the $z_2$ (the upper z) is:
    
$$
\text{left tail area for } z_2 =`r area2_rounded` 
$$

Then using the table again we get left tail area for the $z_1$ (the lower z) is:

$$
\text{left tail area for } z_1 =`r area1_rounded` 
$$

So the area between is:

$$
\text{area between} =`r area2_rounded` - `r area1_rounded` = `r area_between` 
$$

Rounded to the nearest percent this is `r nearest_percent_between`%.
