---
pagetitle: "Normal Right Tail Area"
params:
  mu: 2.3
  sigma: 3.4 
  x: -1.3 
---

```{r}
library("statplosion")
```

```{r}
mu<-params$mu; 
sigma<-params$sigma; 
x<-params$x; 
numer<-(x-mu); 
```

```{r echo=FALSE}
z <- round((x-mu)/sigma,2) 
area <- pnorm(z)
area <- round(area,4)
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```
We have $\mu=`r mu`$, $\sigma=`r sigma`$, and $x = `r x`$:

Here is the picture of the area that we want.    
    
We want the shaded **_right tail area_** which is below the curve and to the right of $x = `r x`$:
     
```{r fig.height=2, fig.width=3, fig.align="center"}
normal_curve(mu,sigma)
normal_shade_right_area(x,mu,sigma)
normal_label_point(x)
```

We will find this area by computing z-value for the given x-value and finding the right tail area for that z-value using the standard normal curve.

Lets find the z-value for the x-value `r x` at edge of the shaded region:

$$
z=\frac{x-\mu}{\sigma}
 =\frac{`r x`-`r mu`}{`r sigma`}
 =\frac{`r numer`}{`r sigma`}
 =`r z` 
$$

So here is the equivalent right tail area when $z=`r z`$. 

```{r fig.height=2, fig.width=3, fig.align="center"}
std_normal_curve()
std_normal_shade_right_area(z)
std_normal_label_point(z)
```
This area is the same size as our original area so we just find this one using the standard normal distribution.     
    
We can find the right tail area for $z=`r z`$ by finding the left tail area and then subtracting that from 1.0.   
    
So lets look up the left tail area first. Go to the row that has `r u` and then to the column that contains `r h` and we see this: 

```{r}
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
make_highlighted_z_huxtable(z, 1)
```

So that means:

$$
\text{left tail area} =`r area` 
$$

This means that the right tail that we want to find is going to be this left tail subtracted from 1.0. 

```{r echo=FALSE}
right_area = 1.0 - area
nearestPercent <- round(right_area*100)
```

$$
\text{right tail area} = 1.0 - `r area` = `r round(right_area,4)` 
$$

Rounded to the nearest percent this is `r nearestPercent`%.
