---
pagetitle: "Sampling Means Right Tail Area"
params:
  mu: 190 
  sigma: 50 
  xbar: 180 
  n: 35 
---

```{r}
library("statplosion")
```

```{r}
mu<-params$mu
sigma<-params$sigma
n<-params$n 
xbar<-params$xbar

stdev <- sigma/sqrt(n)
numer <- xbar-mu

z <- round(numer/stdev,2)
area <- round(pnorm(z),4)
nearestPercent <- round(area*100)
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```

We have $\bar x=`r xbar`$, $\mu =`r mu`$, $\sigma=`r sigma`$ and $n=`r n`$.

We are interested in how likely it is to get a sample mean $\bar x=`r xbar`$ or above for the $\bar x$-distribution.

Here is the $\bar x$-distribution showing the area that we want:    

```{r fig.height=2, fig.width=3, fig.align="center"}
normal_curve(mu, stdev, show=FALSE, axis_label=bquote(bar(x)))
normal_shade_right_area(xbar,mu,stdev)
normal_label_point(xbar)
```

Notice:

- The sample mean $\bar x=`r xbar`$ is at the edge of the shaded region we want to find 
- The population mean $\mu =`r mu`$ is in the center

We want the shaded **_right tail area_** that is to the right of $\bar x = `r xbar`$:

We will find this area by changing the sample mean $\bar x$ into a z-value and then using standard normal table. 

Lets find the z-value using the form of the z-value formula for the $\bar x$-distribution: 

$$
z=\frac{\bar x-\mu}{\frac{\sigma}{\sqrt{n}}}
 =\frac{`r xbar`-`r mu`}{\frac{`r sigma`}{\sqrt{`r n`}}}
 =\frac{`r numer`}{`r sigma/sqrt(n)`}
 =`r z` 
$$

Note that we use the $\sqrt{n}$ in the denominator. This is because we are using the $\bar x$-distribution. 

So here is the equivalent left tail area for of $z=`r z`$. 

```{r fig.height=2, fig.width=3, fig.align="center"}
std_normal_curve()
std_normal_shade_right_area(z)
std_normal_label_point(z)
```

This area is the same size as our original area so we just find this one using the standard normal distribution.

We can find the right tail area for $z=`r z`$ by finding the left tail area and then subtracting that from 1.0.   
    
So lets look up the left tail area first. Go to the row that has `r u` and then to the column that contains `r h` and we see this: 

```{r}
make_highlighted_z_huxtable(z, 1)
```

So that means:

$$
\text{left tail area} =`r area` 
$$

This means that the right tail that we want to find is going to be this left tail subtracted from 1.0. 

```{r echo=FALSE}
right_area = 1.0 - area
nearestPercent <- round(right_area*100)
```

$$
\text{right tail area} = 1.0 - `r area` = `r round(right_area,4)` 
$$

Rounded to the nearest percent this is `r nearestPercent`%. This means the **shaded right tail area corresponds to `r nearestPercent`%** of the entire data. 

This means there is a `r nearestPercent`% chance of getting a sample mean of $\bar x=`r xbar`$ or more for this population when using samples of size $n = `r n`$.
