---
pagetitle: "Sampling Means Left Tail Area"
params:
  mu: 190 
  sigma: 50 
  xbar: 180 
  n: 35 
---

```{r}
library("statplosion")
```

```{r}
mu<-params$mu
sigma<-params$sigma
n<-params$n 
xbar<-params$xbar

stdev <- sigma/sqrt(n)
numer <- xbar-mu

z <- round(numer/stdev,2)
area <- round(pnorm(z),4)
nearestPercent <- round(area*100)
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```

We have $\bar x=`r xbar`$, $\mu =`r mu`$, $\sigma=`r sigma`$ and $n=`r n`$.

We are interested in how likely it is to get a sample mean $\bar x=`r xbar`$ or below for the $\bar x$-distribution here.

Here is the $\bar x$-distribution showing the area that we want:    

```{r fig.height=2, fig.width=3, fig.align="center"}
normal_curve(mu, stdev, show=FALSE, axis_label=bquote(bar(x)))
normal_shade_left_area(xbar,mu,stdev)
normal_label_point(xbar)
```

Notice:

- The sample mean $\bar x=`r xbar`$ is at the edge of the shaded region we want to find 
- The population mean $\mu =`r mu`$ is in the center

We want the shaded **_left tail area_** that is to the left of $\bar x = `r xbar`$:

We will find this area by changing the sample mean $\bar x$ into a z-value and then using standard normal table. 

Lets find the z-value using the form of the z-value formula for the $\bar x$-distribution: 

$$
z=\frac{\bar x-\mu}{\frac{\sigma}{\sqrt{n}}}
 =\frac{`r xbar`-`r mu`}{\frac{`r sigma`}{\sqrt{`r n`}}}
 =\frac{`r numer`}{`r sigma/sqrt(n)`}
 =`r z` 
$$

Note that we use the $\sqrt{n}$ in the denominator. This is because we are using the $\bar x$-distribution. 

So here is the equivalent left tail area for of $z=`r z`$. 

```{r fig.height=2, fig.width=3, fig.align="center"}
std_normal_curve()
std_normal_shade_left_area(z)
std_normal_label_point(z)
```

This area is the same size as our original area so we just find this one using the standard normal distribution.

We can look up the area in the standard normal z-table using $z=`r z`$  
    
We go to the row that has `r u` and then to the column that contains `r h` and we see this: 

```{r}
make_highlighted_z_huxtable(z, 1)
```

So that means:

$$
\text{left tail area} =`r area` 
$$

Rounded to the nearest percent this is `r nearestPercent`%. This means that the **shaded area corresponds to `r nearestPercent`%** of the entire data.

This means there is a `r nearestPercent`% chance of getting a sample proportion of $\bar x=`r xbar`$ or less for the $\bar x$-distribution with sample size of $n=`r n`$.
