---
pagetitle: "Sampling Proportions Left Tail Area"
params:
  count: 190 
  n: 250 
  p: 0.79
---

```{r}
library("statplosion")
```

```{r}
p<-params$p
q<- 1-p
count<-params$count
n<-params$n 
phat<-count/n
stdev <- sqrt((1-p)*p/n)
numer <- phat-p
z <- round(numer/stdev,2)
area <- round(pnorm(z),4)
nearestPercent <- round(area*100)
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```

We have population proportion of $p=`r p`$ and sample proportion of $`r count`$ out of $`r n`$.

We are interested in how likely it is we get our sample proportion or below.

First let's calculate our sample proportion:   

$$
\hat p = \frac{count}{n} = \frac{`r count`}{`r n`} = `r phat`
$$

Before we start we check the conditions of the Central Limit Theorem to make sure we can use a normal distribution here:

$np=(`r n`)(`r p`)= `r n*p`$ and $n(1-p)=(`r n`)(`r q`)= `r n*q`$

Since these are both at least $5$ we are in good shape.

Here is the $\hat p$-distribution showing the area that we want:    

```{r fig.height=2, fig.width=3, fig.align="center"}
normal_curve(p,round(stdev,4), show=FALSE, axis_label=bquote(hat(p)))
normal_shade_left_area(round(phat,4),p,round(stdev,4))
normal_label_point(round(phat,4))
```

Notice:

- The sample proportion $\hat p=`r phat`$ is at the edge of the shaded region we want to find. 
- The population proportion $p =`r p`$ is in the center.

We want the shaded **_left tail area_** that is to the left of $\hat p = `r phat`$:

We will find this area by changing the sample proportion $\hat p$ into a z-value and using the standard normal table. 

First we need the calculation of the standard deviation since we need this in our z-value calculation:

$$
\small{
stdev=\sqrt{\frac{(1-p)p}{n}} 
 =\sqrt{\frac{(1-`r p`)`r p`}{`r n`}}
 =\sqrt{\frac{(`r (1-p)`)`r p`}{`r n`}}
 =\sqrt{\frac{`r (1-p)*p`}{`r n`}}
 =`r stdev`
 }
$$

Now lets find the z-value using the sample proportion $\hat p= `r phat`$ the population proportion $p=`r p`$ and the standard deviation $stdev$ we just found:

$$
z=\frac{\hat p-p}{stdev}
 =\frac{`r phat`-`r p`}{`r stdev`}
 =\frac{`r numer`}{`r stdev`}
 =`r z`
$$

So here is the equivalent left tail area for of $z=`r z`$. 

```{r fig.height=2, fig.width=3, fig.align="center"}
std_normal_curve()
std_normal_shade_left_area(z)
std_normal_label_point(z)
```

This area is the same size as our original area so we just find this one using the standard normal distribution.

We can look up the area in the standard normal z-table using $z=`r z`$  
    
We go to the row that has `r u` and then to the column that contains `r h` and we see this: 

```{r}
make_highlighted_z_huxtable(z, 1)
```

So that means:

$$
\text{left tail area} =`r area`
$$

Rounded to the nearest percent this is `r nearestPercent`%. This means that the **shaded area corresponds to `r nearestPercent`%** of the entire data.

This means there is a `r nearestPercent`% chance of getting a sample proportion of $\hat p=`r phat`$ or less for this population when using samples of size $n = `r n`$.
