---
pagetitle: "Sampling Proportions Right Tail Area"
params:
  count: 190 
  n: 250 
  p: 0.79
---

```{r}
library("statplosion")
```

```{r}
p<-params$p
q<-1-p
count<-params$count
n<-params$n 
phat<-count/n
stdev <- sqrt((1-p)*p/n)
numer <- phat-p
z <- round(numer/stdev,2)
area <- round(pnorm(z),4)
nearestPercent <- round(area*100)
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```

We have population proportion of $p=`r p`$ and sample proportion of $`r count`$ out of $`r n`$.

We are interested in how likely it is we get our sample proportion or above.

First let's calculate our sample proportion:   

$$
\hat p = \frac{count}{n} = \frac{`r count`}{`r n`} = `r phat` 
$$

Before we start we check the conditions of the Central Limit Theorem to make sure we can use a normal distribution here:

$np=(`r n`)(`r p`)= `r n*p`$ and $n(1-p)=(`r n`)(`r q`)= `r n*q`$

Since these are both at least $5$ we are in good shape.

Here is the $\hat p$-distribution showing the area that we want:    

```{r fig.height=2, fig.width=3, fig.align="center"}
normal_curve(p,round(stdev,4), show=FALSE, axis_label=bquote(hat(p)))
normal_shade_right_area(round(phat,4),p,round(stdev,4))
normal_label_point(round(phat,4))
```

Notice:

- The sample proportion $\hat p=`r phat`$ is at the edge of the shaded region we want to find. 
- The population proportion $p =`r p`$ is in the center.

We want the shaded **_right tail area_** that is to the right of $\hat p = `r phat`$:

We will find this area by changing the sample proportion $\hat p$ into a z-value and using the standard normal table. 

First we need the calculation of the standard deviation since we need this in our z-value calculation:

$$
\small{
stdev=\sqrt{\frac{(1-p)p}{n}} 
 =\sqrt{\frac{(1-`r p`)`r p`}{`r n`}}
 =\sqrt{\frac{(`r (1-p)`)`r p`}{`r n`}}
 =\sqrt{\frac{`r (1-p)*p`}{`r n`}}
 =`r stdev` 
 }
$$

Now lets find the z-value using the sample proportion $\hat p= `r phat`$ the population proportion $p=`r p`$ and the standard deviation $stdev$ we just found:

$$
z=\frac{\hat p-p}{stdev}
 =\frac{`r phat`-`r p`}{`r stdev`}
 =\frac{`r numer`}{`r stdev`}
 =`r z` 
$$

So here is the equivalent right tail area for of $z=`r z`$. 

```{r fig.height=2, fig.width=3, fig.align="center"}
std_normal_curve()
std_normal_shade_right_area(z)
std_normal_label_point(z)
```

This area is the same size as our original area so we just find this one using the standard normal distribution.

We can find the right tail area for $z=`r z`$ by finding the left tail area and then subtracting that from 1.0.   
    
So lets look up the left tail area first. Go to the row that has `r u` and then to the column that contains `r h` and we see this: 

```{r}
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
make_highlighted_z_huxtable(z, 1)
```

So that means:

$$
\text{left tail area} =`r area` 
$$

This means that the right tail that we want to find is going to be this left tail subtracted from 1.0. 

```{r echo=FALSE}
right_area = 1.0 - area
nearestPercent <- round(right_area*100)
```

$$
\text{right tail area} = 1.0 - `r area` = `r round(right_area,4)` 
$$

Rounded to the nearest percent this is `r nearestPercent`%. This means the **shaded right tail area corresponds to `r nearestPercent`%** of the entire data. 

This means there is a `r nearestPercent`% chance of getting a sample proportion of $\hat p=`r phat`$ or more for this population when using samples of size $n = `r n`$.
