---
pagetitle: "Solve Backwards Left Tail"
params:
  mu: 18 
  sigma: 3 
  area: .25
---

```{r}
library("statplosion")
```

```{r}
area<-params$area; 
mu<-params$mu; 
sigma<-params$sigma; 
z <- round(qnorm(area),2)
x<-mu + z*sigma
```
We have $\mu=`r mu`$ and $\sigma = `r sigma`$. 

We want an x-value whose **left tail area** is $`r area`$ (or $`r 100*area`\%$). 

Here is what the picture looks like: 

```{r fig.height=2, fig.width=3.5, fig.align="center"}
normal_curve(mu,sigma)
normal_shade_left_area(x,mu,sigma)
normal_label_point(x, label="x=?")
```

To do this we first find the z-value that goes with this same left tail area. It looks like this:

```{r fig.height=2, fig.width=3.5, fig.align="center"}
std_normal_curve()
std_normal_shade_left_area(z)
std_normal_label_point(z, label="z=?")
```

We use the table backwards and look for the closest z-value to our area `r area`. We may not find it exactly so we look for the entry that is closest to `r area`.
    
```{r}
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
make_highlighted_z_huxtable(z, 1)
```

We get this z-value: 

$$ 
z = `r z` 
$$

Then we can find the x-value by plugging in the z-value and the $\mu=`r mu`$ and $\sigma = `r sigma`$ (which were given) and solving for x: 

\begin{align} 
z &= \frac{x-\mu}{\sigma} \\
`r z` &= \frac{x-`r mu`}{`r sigma`} \\
`r sigma`(`r z`) &= x-`r mu` \\
`r sigma*z`+ `r mu` &= x \\ 
`r x` &= x
\end{align}

_**Steps to solve for x:**_

1. Plug in $\mu=`r mu`$, $\sigma=`r sigma`$ and $z=`r z`$
2. Multiple by $`r sigma`$ on both sides
3. Add $`r mu`$ to both sides as well

This gives us the x-value that we need. Here is the graph:

```{r fig.height=2, fig.width=3, fig.align="center"}
normal_curve(mu,sigma)
normal_shade_left_area(x,mu,sigma)
normal_label_point(x)
```

So $x=`r x`$ is the x-value that has a left tail area of $`r 100*area`$%. 

