---
pagetitle: "Std Normal Area Between Spreadsheet"
params:
  z1: -0.54
  z2: 1.24
---

```{r, include=F}
library("statplosion")
z1<-params$z1; 
z2<-params$z2; 
```
```{r echo=FALSE}
area1_actual <- pnorm(z1)
area1_rounded <- round(area1_actual,4)
nearest_percent1 <- round(area1_rounded*100)

area2_actual <- pnorm(z2)
area2_rounded <- round(area2_actual,4)
nearest_percent2 <- round(area2_rounded*100)

area_between <- area2_rounded - area1_rounded
nearest_percent_between <- round(area_between*100)
```

Here is the picture of the area we want.  

```{r fig.height=2, fig.width=3.5, fig.align="center"}
std_normal_curve()
std_normal_shade_area_between(z1,z2)
std_normal_label_point(z1)
std_normal_label_point(z2)
```

We want the shaded region to the left of $z_2=`r z2`$ and to the right of $z_1 = `r z1`$

We will calculate this area using a spreadsheet and the **NORMSDIST** function. 

Since **NORMSDIST** gives us left tails we look up the left tail area for the greater z-value $z_2$ and subtract the left tail area for the lesser z-value $z_1$.

- Type **z1** in cell **B2** 
- Then type $`r z1`$ into **C2**
- Type **z2** in cell **B3** 
- Then type $`r z2`$ into **C3**

```{r}
spread<-create_hux_spreadsheet(5,4)
spread<-set_hux_spreadsheet_val(spread, "z1", col="B", row=2) 
spread<-set_hux_spreadsheet_val(spread, z1, col="C", row=2) 
spread<-set_hux_spreadsheet_val(spread, "z2", col="B", row=3) 
spread<-set_hux_spreadsheet_val(spread, z2, col="C", row=3) 
spread
```
    
- Then type in **area between** in **B4**, 
- In cell **C4** enter **=NORMSDIST(C3)-NORMSDIST(C2)**, and then hit enter
    
```{r}
spread<-set_hux_spreadsheet_val(spread, "area between", col="B", row=4) 
spread<-set_hux_spreadsheet_val(spread, "=NORMSDIST(C3)-NORMSDIST(C2)", col="C", row=4) 
spread
```

After hitting enter you should see the result as follows:

```{r}
spread<-set_hux_spreadsheet_val(spread, area_between, col="C", row=4) 
spread
```

Rounded to the nearest percent this is `r nearest_percent_between`%. 

This means that the shaded area corresponds to `r nearest_percent_between`% of the entire data.
