---
pagetitle: "Std Normal Left Tail Area"
params:
  z: 1.23
---

```{r}
library("statplosion")
z<-params$z; 
```

```{r echo=FALSE}
area <- pnorm(z)
nearestPercent <- round(area*100)
area <- round(area,4)
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```
We have $z = `r z`$. 

Here is the picture of the area we want.  

```{r fig.height=2, fig.width=3.5, fig.align="center"}
std_normal_curve()
std_normal_shade_left_area(z)
std_normal_label_point(z)
```

We want the shaded region to the left of $z=`r z`$

If we look up the area in the standard normal z-table using  $z=`r z`$ we go to the row that has `r u` and then to the column that contains `r h` and we see this: 

```{r}
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
make_highlighted_z_huxtable(z, 1)
```
So that means:

$$
\text{left tail area} =`r area` 
$$

Rounded to the nearest percent this is `r nearestPercent`%. This means that the shaded area corresponds to `r nearestPercent`% of the entire data.
