---
pagetitle: "Std Normal Left Tail Area Spreadsheet"
params:
  z: 1.23
---

```{r, include=F, echo=F}
knitr::opts_chunk$set(echo = FALSE)
library("statplosion")
z<-params$z
```

```{r}
area <- pnorm(z)
nearestPercent <- round(area*100)
area <- round(area,4)
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
```
We have $z = `r z`$. 

Here is the picture of the area we want.  

```{r}
#| fig-height: 3
#| fig-width: 5 
#| fig-cap: "This is the left tail area we want."
#| fig-cap-postion: margin 
std_normal_curve()
std_normal_shade_left_area(z)
std_normal_label_point(z)
```

We want the shaded region to the left of $z=`r z`$. We will calculate this area using a spreadsheet and the **NORMSDIST** function which gives left tail areas for z-values. 

- Type **z** in cell **B2** 
- Then type $`r z`$ into **C2**

::: {style="width:50%;margin:auto"}
```{r}
#| tbl-cap: Enter the z-value 
spread<-create_hux_spreadsheet(4,4)
spread<-set_hux_spreadsheet_val(spread, "z", col="B", row=2) 
spread<-set_hux_spreadsheet_val(spread, z, col="C", row=2) 
spread
```
:::
    
- Then type in **left tail area** in **B3**, 
- In cell **C3** type **=NORMSDIST(** then click on **C2** then type **)** then hit enter 
    
::: {style="width:50%;margin:auto"}
```{r}
#| tbl-cap: Enter the NORMSDIST formula
spread<-set_hux_spreadsheet_val(spread, "left tail area", col="B", row=3) 
spread<-set_hux_spreadsheet_val(spread, "=NORMSDIST(C2)", col="C", row=3) 
spread
```
:::

::: {style="width:50%;margin:auto"}

```{r}
#| tbl-cap: After entering you should see the result
spread<-set_hux_spreadsheet_val(spread, area, col="C", row=3) 
spread
```
:::

Rounded to the nearest percent this is **`r nearestPercent`%**.

This means that the left tail area for $z=`r z`$ is **`r nearestPercent`%**.
