---
pagetitle: "Std Normal Right Tail Area Spreadshet"
params:
  z: -1.34 
---

```{r, include=F}
library("statplosion")
z<-params$z; 
```
```{r echo=FALSE}
left_tail_area <- pnorm(z)
left_tail_area_table <- round(left_tail_area,4)

right_tail_area <- 1.0 - left_tail_area_table
nearestPercent <- round(right_tail_area*100)
```
We have $z = `r z`$. 

Here is the picture of the area we want.  

```{r fig.height=2, fig.width=3.5, fig.align="center"}
std_normal_curve()
std_normal_shade_right_area(z)
std_normal_label_point(z)
```

We want the shaded region to the right of $z=`r z`$. 

We will calculate this area using a spreadsheet and the **NORMSDIST** function but because **NORMSDIST** finds left tails we have to use a trick. We actually will find the left tail area for this z-value, then subtract from 1.0 to get our right tail area. 

- Type **z** in cell **B2** 
- Then type $`r z`$ into **C2**

```{r}
spread<-create_hux_spreadsheet(4,4)
spread<-set_hux_spreadsheet_val(spread, "z", col="B", row=2) 
spread<-set_hux_spreadsheet_val(spread, z, col="C", row=2) 
spread
```
    
- Then type in **right tail area** in **B3**, 
- In cell **C3** type **=1.0-NORMSDIST(** then click on **C2** and then type **)** then hit enter
    
```{r}
spread<-set_hux_spreadsheet_val(spread, "right tail area", col="B", row=3) 
spread<-set_hux_spreadsheet_val(spread, "=1.0-NORMSDIST(C2)", col="C", row=3) 
spread
```
After hitting enter you should see the result as follows:

```{r}
spread<-set_hux_spreadsheet_val(spread, right_tail_area, col="C", row=3) 
spread
```

Rounded to the nearest percent this is **`r nearestPercent`%**.

This means that the right tail area for $z=`r z`$ is **`r nearestPercent`%**.
