---
pagetitle: "Histogram"
params:
  n: 14
---

```{r}
n <- params$n
main <- paste0("Histogram of ", n, " data values")
values <- sample(c(2, 3, 4, 2, sample(1:8, n-4, replace=TRUE)))
```

First we choose $n=`r n`$ random data values in the interval $[1,10]$:

`r values`

Now here is a histogram showing the data:
```{r fig.height=3, fig.width=4, fig.align='center'}
hist(values, breaks=c(0,2,4,6,8,10), main=main)
```

```{r echo=F}
h<-hist(values, breaks=c(0,2,4,6,8,10), plot=F)
whichbin<-"endpoints 0 to 2"
count<-h$counts[2]
perc<-round(h$counts[2]/n,2)*100 
v <- values[(values>2) & (values <=4)]
```

**Question**:    
From this graph, determine whether a data value of 2 is included in the first bin (with endpoints 0 and 2) or the second bin from (with endpoints 2 and 4).  

**Answer**:    
**in the bin with endpoints 0 to 2**

**Question**:    
Find the count of values in the bin with endpoints 2 and 4.  
    
**Answer**:   
**`r count`**  

**Question**:    
List all the data values (including repetitions) that are in the bin with endpoints 2 to 4.   

**Answer**:   
**`r v`**

**Question**:    
Find the percentage of data values in the bin with endpoints 2 and 4.  

**Answer** :   
**`r perc`%**
