---
pagetitle: "Kable"
params:
  z: -1.25
---

```{css, eval=T,echo=F}
table.table {
    width: auto !important;
}
table {
      width: auto !important;
	  margin: auto !important;
	  border-top: 3px solid #666 !important;
	  border-bottom: 3px solid #666 !important;
	  margin-bottom: 20px !important;
}
table thead th { 
border-bottom: 3px solid #ddd !important; 
}
th, td { 
    	width: auto !important;
	border: 1px solid #666 !important;
	padding: 5px !important; 
	height: 30px !important;
	min-width: 50px !important;
}
```

```{r}
library("statplosion")
library("kableExtra")
```

```{r}
z<-params$z
z_rounded<-as.numeric(round_and_format_z(z))
parts <- extract_tenths_and_hundredths(z)
u <- parts[1]
h <- parts[2]
a <- round(pnorm(z_rounded),4)
nearestPercent <- round(a*100)
```

We have $z=`r z`$.

Below is a picture of the area. We want to know how big the shaded area is. In particular if the whole area under the curve is 100%, how big is the shaded part? 

```{r fig.height=2, fig.width=3, fig.align="center"}
std_normal_curve()
std_normal_shade_left_area(z)
std_normal_label_point(z)
```

We start by going to the row that has $z=`r u`$ and then we go over to the column that is $`r h`$. The left tail area is where the row and column meet. 

```{r}
colnames(df)
rownames(df)
print(u)
print(h)
extra_rows<-3
df<-make_z_dataframe(z,3)
areadf<-make_area_dataframe(df)

#entry is in 4,2

maxrow <- 7
maxcol <- 10

i=7
j=10


format<-NULL
if(knitr::is_latex_output()) {
    format <- "latex"
} else if(knitr::is_html_output()) {
    format <- "html"
}

print(format)

areadf[i,j]<-cell_spec(areadf[i,j], "html", bold=T, color='white',background="black")
if(i>1) {
    for(row in 1:(i-1)) {
        print("here here")
        areadf[row,j]<-cell_spec(areadf[row,j], format=format, background="lightgray")
    }
}
if(j>1) {
    for(col in 1:(j-1)) {
        print("here")
        print(col)
        areadf[i,col]<-cell_spec(areadf[i,col], format=format, background="lightgray")
    }
}

kable(areadf, format=format, escape=F)


```


```{r}
# df<-head(iris, 5)
# v <- c(TRUE, TRUE, TRUE, FALSE, FALSE)
# print(df$Petal.Length>1.3)
# kable(df) %>%
#   row_spec(2, background = ifelse(v,"black","green"))
```

So we have this:
\begin{equation}
\text{left tail area} =`r a` `r example_label("lefttailarea")`
\end{equation}

Rounded to the nearest percent this is $`r nearestPercent`$%. The shaded region represents about $`r nearestPercent`$% of the entire area.
